### 2016-07-07 reasoning.tex
Footnote edit for KC.

We now describe a proof system that lets us demonstrate that a \txnimp
program satisfies its high-level invariants in all small-step
executions that satisfy a chosen trace invariant ($\I$).\footnote{It is
important to keep in mind the distinction between high-level invariants
(\eg~\C{X$\ge$0}) and trace invariants (\eg~\C{RC}). The former
constitute \emph{proof} \emph{obligations} for the programmer, whereas
the latter captures \emph{assumptions} about the operational characteristics
of transactions and the underlying data store. } 
Since the trace invariant captures transaction-isolation constraints,
the demonstration is a proof that the given selection of isolation
levels for transactions is sufficient to enforce a program's invariants.

>>>>

We now describe a proof system that lets us demonstrate that a \txnimp
program satisfies its high-level invariants in all small-step
executions that satisfy a chosen trace invariant ($\I$).\footnote{It is
important to keep in mind the distinction between high-level invariants
(\eg~\C{X$\ge$0}) and trace invariants (\eg~$\I =
\lambda\E.\,\C{RC}(\C{Wd1})\wedge \C{SI}(\C{Wd2})$). The former
constitute \emph{proof} \emph{obligations} for the programmer, whereas
the latter is a combination of transaction-specific \emph{assumptions} about 
operational characteristics of the underlying data store. } 
Since the trace invariant captures transaction-isolation constraints,
the demonstration is a proof that the given selection of isolation
levels for transactions is sufficient to enforce a program's invariants.
